---
title: "Figure 2: Variability decomposition"
author: "Nicholas A. Coles"
date: "2025-04-01"
output: html_document
editor_options: 
  chunk_output_type: console
---
This code is designed to (a) estimate the extent to which the effects of gratitude tasks exhibit heterogeneity across different interventions and countries, (b) illustrate the heterogeneity via density curves, and (c) illustrate observed patterns via a second illustration that is combined via ggExtra.

The code as it is written creates this plot for a single independent variable: Pa_effect size. It needs to into a function that can produce the plot for any given variable. This will allow us, for instance, to use lapply to generate plots for pa_effects_size, na_effect_size, optimism_effect_size, ls_effect_size (combined with highly correlated ladder_effect_size), envy_effect_size, and indebted_effect_size.

Once these outcome-specific figures are created via the function (e.g,. via lapply), they can be combined via ggExtra for the final version of the Figure.

Please functionalize the code.

Load libraries
```{r lib}
library(tidyverse)
library(metafor)
library(ggExtra)
library(ggplot2)
library(ggrepel)
library(cowplot)
library (here)
```

Prep data
```{r}
# specify directory
i_am("code/Figure2.Rmd")

# open data
df <- 
  read.csv(file = here("data",'unique_country_effect_sizes.csv'))

# estimate total heterogeneity
m <-  
  rma(yi = pa_effect_size,
      vi = pa_var,
      data = df)

# estimate between-country heterogeneity
m.c <-
  rma.mv(yi = pa_effect_size,
         V = pa_var,
         random = ~ 1 | country,
         data = df)

# estimate between-intervention heterogeneity
m.i <-
  rma.mv(yi = pa_effect_size,
         V = pa_var,
         random = ~ 1 | intervention_condition,
         data = df)

# simultaneously estimate between-country and between-intervention heterogeneity
m.ic <-
  rma.mv(yi = pa_effect_size,
         V = pa_var,
         random = list(~ 1 | intervention_condition, ~ 1 | country),
         data = df)

# more between-country than between-intervention heterogeneity
## total het
m$tau2 %>% sqrt()

## country-level het
m.c$sigma2 %>% sqrt()

## intervention-level het
m.i$sigma2 %>% sqrt()

# similar pattern when modeled together
m.ic$sigma2[2] %>% sqrt()

## P.S. This is a fun statistical oddity that illustrates that the hierarchical meta-analyses overestimate variance (because they're designed to have conservative statistical properties that reduce Type I error). It's a fun footnote at best: the statistical properties of this (very commonly used and oft-respected) method make it such that we can (a) more accurately estimate variance decomposition proportions, but at the expense of (b) overestimating the magnitude of this variance
m$tau2 < sum(m.c$sigma2,m.i$sigma2)
m$tau2 < sum(m.ic$sigma2)
rm(m, m.i, m.c)
```

# Calculate country-level and intervention-level descriptives
```{r}
# country-level descriptives
d.c <-
  df %>% 
  group_by(country) %>% 
  summarise(m = mean(pa_effect_size)) %>% 
  
  # add [jittered] y-value to assist with plotting
  mutate(y = 0,
         y = jitter(y, .1)) %>% 
  
  # labels most extreme observations (in terms of min and max)
  mutate(label = 
           if_else(m == min(d.c$m),
                   true = country,
                   false = ""),
         label = if_else(m == max(d.c$m),
                         true = country,
                         false = label))

# intervention-level descriptives
d.i <-
  df %>% 
  group_by(intervention_condition) %>% 
  summarise(m = mean(pa_effect_size)) %>% 
  
  # add [jittered] y-value to assist with plotting
  mutate(y = -.02,
         y = jitter(y, .1)) %>% 
  
  # labels most extreme observations (in terms of min and max)
  mutate(label = 
           if_else(m == min(d.i$m),
                   true = intervention_condition,
                   false = ""),
         label = if_else(m == max(d.i$m),
                         true = intervention_condition,
                         false = label))
```

# Create density plots
```{r}
m.d <-
  ggplot() +
  
   # add overall effect size estimate
   geom_point(aes(x = m.ic$b[1], # overall effect in fullest model (m.ic)
                  y = 5.7),
              
              # aesthetics
              shape = 18,
              size = 4,
              color = "grey30") +
   
   # add 95% CI of overall effect size estimate
   geom_segment(aes(x = m.ic$ci.lb,
                    xend = m.ic$ci.ub,
                    y = 5.7),
                
                # aesthetics
                color = "grey30") +

  # density plot: intervention-level sources of heterogeneity
  ## mean = overall effect
  ## sd = first estimate of sigma2
  stat_function(fun = dnorm, 
                args = list(mean = m.ic$b[1], 
                            sd = m.ic$sigma2[1] %>% 
                              sqrt()), 
                color = "#E64B35") +
  
  # country-level sources of heterogeneity
  ## mean = overall effect
  ## sd = second estimate of sigma2
  stat_function(fun = dnorm, 
                args = list(mean = m.ic$b[1], 
                            sd = m.ic$sigma2[2] %>% 
                              sqrt()), 
                color = "#3C5488") +
  
  # aesthetics
  scale_x_continuous(limits = c(-1, 1)) +
  scale_y_continuous(limits = c(0, 6)) +
  theme_void() +
  ggtitle(" Positive affect") 
```

# Plot descriptives
```{r}
m.p <-
  ggplot() +

  # add country-level descriptives
  geom_point(data = d.c,
              aes(x = m, 
                  y = y), 
             
             # aesthetics
             color = "#3C5488",
             alpha = .5) +
  
  # add labels
  geom_text_repel(data = d.c,
                  aes(x = m,
                      y = y,
                      label = label),
                  
                  # aesthetics
                  color = "#3C5488",
                  alpha = .5,
                  nudge_y = -.01) +
  
  # plot intervention-level descriptives
  geom_point(data = d.i,
              aes(x = m, 
                  y = y),
             
             # aesthetics
             color = "#E64B35",
             alpha = .5) + 
  
  # add labels
  geom_text_repel(data = d.i,
              aes(x = m, 
                  y = y,
                  label = label),
             
              # aesthetics
             color = "#E64B35",
             alpha = .5,
             nudge_y = .01) +
  
  # aesthetics
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank()) +
  scale_x_continuous(limits = c(-.3, 1)) +
  labs(x = expression("Cohens " * italic('d')))
```

# combine plots
```{r}
plot_grid(m.d,
          m.p, 
          ncol = 1, 
          rel_heights = c(.5, 1))
```
