---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
# set up packages
library(here)
library(tidyverse)
library(qualtRics)
library(psych)
library(gridExtra)
library(lme4)
library(lmerTest)
library(emmeans)

# allow for Type III Sums of Square
options(contrasts = c('contr.sum', 'contr.poly'))
```

# Open data
```{r}
# Dangs API credential at UCSD
qualtrics_api_credentials(
  api_key = 'urh7PtWEEOkAzrbjmYQC2FoipCvCT4n8ZIByL5rH', 
  base_url = 'iad1.qualtrics.com',
  install = TRUE,
  overwrite = TRUE)

readRenviron("~/.Renviron")

# open data
DF <- fetch_survey(surveyID = 'SV_1YQ3FmlbEHp1RIO',
                   force_request = T,
                   label = F,
                   convert = F)

# process data
DF <- DF %>%
  
  # remove incomplete or test observations
  filter(DistributionChannel != "preview",
         Progress > 95,
         consent == 1,
        
        #TUR_01 test data
         ResponseId != "R_42KUGZSS76NgWH7",
         ResponseId != "R_4W4EXfgeyk1rCYF",
         ResponseId != "R_45Z862EIfzYcin4",
         ResponseId != "R_7BhJx9Ci7THupmF",
         ResponseId != "R_42Lv9fg5qi9V9xm",
         ResponseId != "R_2kFa26mh78uevnz",
         ResponseId != "R_4DRThnH8LgbEvM8",
         ResponseId != "R_4r1kAEqQCo1PNn6",
         ResponseId != "R_4GQErqyYDlRWVwZ",
         ResponseId != "R_4SGF0GCHSHIN0ls",
         ResponseId != "R_6Pndj5c7sr1pcU3",
         ResponseId != "R_8lQxsY2ITg7HKh1",
        
        #USA_01 duplicate data
        ResponseId != "R_6rDfD5u84z6WufT",
        
        #ESP_01 duplicate data
        ResponseId != "R_27FP7RxRpESO3F7") %>% 
  
  # select relevant variables
  select(Status: envy_DO_envy_8,
         lab : condition_type,
         me_attention, meals_attention) %>% 
  
  # fix variable formatting
  mutate_at(c('ResponseId', 'lab',
              'condition', 'condition_type'),
            as.factor)
```

# Examine reliability
```{r}
rel <- 
  sapply(X = DF$lab %>% unique() %>% as.character(),
         simplify = F,
         USE.NAMES = T,
         FUN = function(x){
           d <- DF %>%
             filter(lab == x)
           
           # gratitude
           gra <- psych::alpha(x = d %>%
                                 select(grateful, appreciative, thankful))$total[1] %>% 
             as.numeric()
           
           # positive affect
           pas <- psych::alpha(x = d %>%
                                 select(happy, satisfied, content, joyful, pleased))$total[1] %>% 
             as.numeric()
           
           # optimism
           opt <- psych::alpha(x = d %>%
                                 select(optimistic, hopeful))$total[1] %>% 
             as.numeric()
           
           # negative affect
           neg <- psych::alpha(x = d %>%
                                 select(sad, depressed, anxious, nervous))$total[1] %>% 
             as.numeric()
           
           # indebtedness
           ind <- psych::alpha(x = d %>%
                                 select(indebted, obligated))$total[1] %>% 
             as.numeric()
           
           # envy
           env <- psych::alpha(x = d %>%
                                 select(envious, bitter, jealous))$total[1] %>% 
             as.numeric()
           
           # life satisfaction
           lif <- psych::alpha(x = d %>%
                                 select(ls_1, ls_2, ls_3, ls_4, ls_5))$total[1] %>% 
             as.numeric()
           
           # sense of self
           sen <- psych::alpha(x = d %>%
                                 select(self_image_circle, self_image))$total[1] %>% 
             as.numeric()
           
           list(
             gra = gra,
             pas = pas,
             opt = opt,
             neg = neg,
             ind = ind,
             env = env,
             lif = lif
           ) %>%
             return()
       }
       )


# 7 is having problems w/ optimism and envy (NGA_02)
# 8 is having problems with envy (NGA_01)
# 3 (TUR_01) is having problems with indebtedness
rel <- rel %>% bind_rows()
```

# Calculate scales
```{r}
DF <- DF %>% 
  rowwise() %>% 
  mutate(
    # gratitude
    gratitude_mean = 
      mean(c(grateful, appreciative, thankful), 
           na.rm = T),
    
    # positive affect
    pa_mean = 
      mean(c(happy, satisfied, content, joyful, pleased), 
           na.rm = T),
    
    # optimism
    optimistic_mean = 
      mean(c(optimistic, hopeful), 
           na.rm = T),
  
    # negative affect
    na_mean = 
      mean(c(sad, depressed, anxious, nervous), 
           na.rm = T),
    
    # indebtendess
    indebted_mean = 
      mean(c(indebted, obligated), 
           na.rm = T),
          
    # envy
    envy_mean = 
      mean(c(envious, bitter, jealous), 
           na.rm = T),
    
    # life satisfaction
    ls_mean = 
      mean(c(ls_1, ls_2, ls_3, ls_4, ls_5), 
           na.rm = T),
    
    # sense of self
    ss_mean = 
      mean(c(self_image_circle, self_image), 
           na.rm = T)) %>% 
  ungroup()
  
# delete vestigial variables
DF <- DF %>%
  select(-c(grateful, appreciative, thankful, 
            happy, satisfied, content, 
            joyful, pleased, optimistic,
            hopeful,  depressed, sad,  anxious,  nervous,
            indebted, obligated,
            envious, bitter, jealous,
            ls_1, ls_2, ls_3,
            ls_4, ls_5, self_image_circle,
            self_image)
         )
```

# visualize distributions of each outcome
```{r}
DF %>%
  
  # pivot into long format so that we can facet
  pivot_longer(cols = c(gratitude_mean : ss_mean),
               names_to = "outcomes",
               values_to = "value") %>%
  
  # create ggplot
  ggplot(data = .,
         aes(x = value,
             fill = condition_type,
             colour = condition_type)) +
  
  # facet by outcome
  facet_wrap(~ outcomes) +
  
  # density plot
  geom_density(alpha = .3) +
  
  # aes
  theme_classic()
```

# Analyses
## Simple pre-analyses
```{r}
# create list of outcome variables
out.list <- c('gratitude_mean',
              'pa_mean',
              'optimistic_mean',
              'na_mean',
              'indebted_mean',
              'envy_mean',
              'ls_mean',
              'ss_mean')

# for each outcome build model
results <- sapply(X = out.list,
                  simplify = F,
                  FUN = function(x){
                    
                    m <- lmer(as.formula(paste0(x, 
                                                '~ condition_type + (1 + condition_type | lab)')
                                         ),
                              data = DF) %>%
                      summary()
                    
                    return(m)
       })

# simplify models due to singular fit
results2 <- sapply(X = out.list,
                  simplify = F,
                  FUN = function(x){
                    
                    m <- lmer(as.formula(paste0(x, 
                                                '~ condition_type + (1 | lab)')
                                         ),
                              data = DF) %>%
                      summary()
                    
                    return(m)
       })
```

## Pre-registered analyses
```{r}
# for each outcome build model
results3 <- sapply(X = out.list,
                  simplify = F,
                  FUN = function(x){
                    
                    m <- lmer(as.formula(paste0(x, 
                                                '~ condition + (1 + condition | lab)')
                                         ),
                              data = DF)
                    
                    emm <- emmeans(m,
                                   pairwise ~ condition,
                                   pbkrtest.limit = 9999)
                    
                    return(list(m = summary(m), 
                                emm = emm)
                           )
       })

# simplify models due to convergence issues
results4 <- sapply(X = out.list,
                  simplify = F,
                  FUN = function(x){
                    
                    m <- lmer(as.formula(paste0(x, 
                                                '~ condition + (1  | lab)')
                                         ),
                              data = DF)
                    
                    emm <- emmeans(m,
                                   pairwise ~ condition,
                                   pbkrtest.limit = 9999)
                    
                    return(list(m = summary(m), 
                                emm = emm)
                           )
       })
```

# Thought for Annabel (Sep 5)
Derive the estimated overall effect and between-country variability for each one of the conditions.

# Checks
Mike: what happens if we compare the strongest conditions?
```{r}
DF %>% 
  filter(condition == 'letter' |
           condition == 'text' |
           condition == 'measure') %>% 
  group_by(condition) %>% 
  summarise(m = mean(gratitude_mean,
                     na.rm = T),
            sd = sd(gratitude_mean,
                    na.rm = T),
            n = n())
```

Nicholas (05/10 and 16): Let's look at areas where we have higher quality data (less dropout)
```{r}
DF %>% 
  filter(lab == 'USA_02',
         condition == 'letter' |
           condition == 'text' |
           condition == 'measure') %>% 
  group_by(condition) %>% 
  summarise(m = mean(gratitude_mean,
                     na.rm = T),
            sd = sd(gratitude_mean,
                    na.rm = T),
            n = n())
```

Nicholas (05/17): Prolific data
```{r}
# get measurement only descriptives
meas.desc <- DF %>% 
  filter(lab == 'USA_02',
         condition == 'measure',
         meals_attention == 4) %>% 
  summarise(m = mean(gratitude_mean,
                     na.rm = T),
            sd = sd(gratitude_mean,
                    na.rm = T),
            n = n())

# get gratitude condition descriptives
grat.desc <- DF %>%
  # filter out non-measure controls
  filter(lab == 'USA_02',
         condition_type == 'intervention',
         meals_attention == 4) %>%
  
  # get condition-specific M, SD, and n
  group_by(condition) %>%
  summarise(m = mean(gratitude_mean,
                     na.rm = T),
            sd = sd(gratitude_mean,
                    na.rm = T),
            n = n()) %>% 
  ungroup() 
  
# calculate Cohen's d
d.list <- grat.desc %>% 
  rowwise() %>% 
  mutate(d = 
           (m - meas.desc$m) / 
           sqrt(
             ((sd^2 + meas.desc$sd^2) / 2)
             ) 
         ) %>% 
  ungroup() %>% 
  mutate(m = round(m, 2),
         sd = round(sd, 2),
         d = round(d, 2)) %>% 
  arrange(-m)
```

Nicholas (05/17): Prolific data (with attention check removed)
```{r}
# get measurement only descriptives
meas.desc <- DF %>% 
  filter(lab == 'USA_02',
         condition == 'measure',
         meals_attention == 4) %>% 
  summarise(m = mean(gratitude_mean,
                     na.rm = T),
            sd = sd(gratitude_mean,
                    na.rm = T),
            n = n())

# get gratitude condition descriptives
grat.desc <- DF %>%
  # filter out non-measure controls
  filter(lab == 'USA_02',
         condition_type == 'intervention',
         meals_attention == 4) %>%
  
  # get condition-specific M, SD, and n
  group_by(condition) %>%
  summarise(m = mean(gratitude_mean,
                     na.rm = T),
            sd = sd(gratitude_mean,
                    na.rm = T),
            n = n()) %>% 
  ungroup() 
  
# calculate Cohen's d
d.list <- grat.desc %>% 
  rowwise() %>% 
  mutate('d (compared to measure only)' = 
           (m - meas.desc$m) / 
           sqrt(
             ((sd^2 + meas.desc$sd^2) / 2)
             ) 
         ) %>% 
  ungroup()
```

```{r}
DF[DF$lab == "USA_02", ]$me_attention %>% unique()
```

